---
title: "STAT 33B Homework 3"
date: "Oct 8, 2020"
author: "Yuanrui Zhu (3034615728)"
output:
  pdf_document:
    latex_engine: xelatex
---

This homework is due __Oct 8, 2020__ by 11:59pm PT.

Homeworks are graded for correctness. 

As you work, write your answers in this notebook. Answer questions with
complete sentences, and put code in code chunks. You can make as many new code
chunks as you like.

Please do not delete the exercises already in this notebook, because it may
interfere with our grading tools.

You need to submit your work in two places:

* Submit this Rmd file with your edits on bCourses.
* Knit and submit the generated PDF file on Gradescope.

If you have any last-minute trouble knitting, **DON'T PANIC**. Submit your Rmd
file on time and follow up in office hours or on Piazza to sort out the PDF.


The Bay Area Vehicles Data Set
==============================

The Bay Area Vehicles Data Set is a collection of advertisements for vehicles
for sale in the San Francisco Bay Area. The data set was collected from the
website Craigslist on Sep 28, 2020.

The data set is available on the bCourse as `2020.09_cl_vehicles.rds`.

Each row is one advertisement. The columns are:

* `title`: title of advertisement
* `text`: full text of advertisement
* `latitude`: latitude of vehicle
* `longitude`: longitude of vehicle
* `city_text`: city listed in advertisement
* `date_posted`: date advertisement was posted
* `date_updated`: date advertisement was updated, if any
* `price`: price in US dollars
* `vin`: vehicle identification number (like a serial number)
* `condition`: condition, as a category
* `drive`: type of drivetrain
* `fuel`: type of fuel used
* `odometer`: odometer reading, in miles
* `transmission`: type of transmission
* `type`: type of vehicle (sedan, truck, van, etc.)
* `year`: year vehicle was manufactured
* `make`: brand of vehicle
* `model`: model of vehicle
* `craigslist`: craigslist region where advertisement was posted
* `place`: place name (like city, but also includes small towns) based on
  latitude/longitude
* `city`: city based on latitude/longitude
* `state`: state based on latitude/longitude
* `county`: county based on latitude/longitude

Many of the columns were programmatically extracted from the `title` and
`text`, so there may be missing or incorrect values.


Exercise 1
==========

Read the vehicles data set into R, then use R functions to answer the
following:

1. How many advertisements are there?

2. Which columns are categorical but aren't factors? Convert these to factors.

   _Hint 1: Remember that categorical features are usually qualitive and have a
   limited set of possible values._

   _Hint 2: You can use subsetting and `lapply()` to convert many columns at
   once._

3. What percentage of each column is missing? Which columns have a lot of
   missing values?

   _Hint 1: Call `is.na()` on each column, then use `colSums()`._

   _Hint 2: Yes, the second question is a little bit vague. Think of it as the
   sort of casual question a supervisor might ask you in an industry job. Your
   answer should clarify how you interpreted "a lot of missing values"._

**YOUR ANSWER GOES HERE:**



```{r}
vehicles = readRDS("2020.09_cl_vehicles.rds")
# Q1 number of advertisements
nrow(vehicles)

# Q2 columns that aren't factors
lapply(vehicles, is.factor)
# from the result we can see that "city text", "condition", "drive", "fuel", "transmission", 
# "type", "craigslist" are factors
summary(vehicles)
str(vehicles)
# from the summary we can see that "city text", "condition", "drive", "fuel", 
# "transmission", "type", "craigslist", "make", "model", "place", "city", 
# "state", "country", "year" are categorical
# as a result, "make", "model", "place", "city", "state", "country", "year" are categorical but not factors
# convert the above to factors
cols = c("make", "model", "place", "city", "state", "county")
vehicles[cols] = lapply(vehicles[cols], as.factor)

#Q3 missing values
colSums(is.na(vehicles)) / nrow(vehicles)
# from the table I created, I can see that "date_updated", "vin", "condition", 
#"city" all have a lot of missing values, 
# with "a lot" being defined as more than 20% of the total data missing
```

Exercise 2
==========

1. Compute the number of missing values in each row.

   _Hint 1: Call `is.na()` on each row._

   _Hint 2: Some of the apply functions transpose the results. The `dim()`
   function is one way to check._

2. Use ggplot2 to make a bar plot of the numbers from from part 1. Make sure to
   put an appropriate title and labels on your plot.

   _Hint: You can create a data frame with the `data.frame()` function._

3. When a row in this data set has missing values, does it tend to have a lot
   of missing values, or only a few?

**YOUR ANSWER GOES HERE:**

```{r}
#Q1
row_missing = rowSums(is.na(vehicles))

#Q2
#install.packages("ggplot2")
library(ggplot2)
ggplot(data.frame(row_missing), aes(x = row_missing)) + geom_bar()

#Q3
# from the bar chart we can see the majority of missing values lies around 2 and 3, 
# so in terms of the total number of columns (number of elements within a row), 
# a row tend to have only a few missing values
```


Exercise 3
==========

Make a box plot of `odometer` readings, broken down by the `condition` of the
vehicle. Remove any extreme `odometer` values, so that it is easy to compare
the boxes.

Comment briefly on the distribution of odometer readings for the various
conditions.

_Hint: There are several ways to identify extreme values. One way is to make a
box plot. Another way is to find values above a certain percentile
(`quantile()`), say 99%. Yet another way is to find values more than 2-3
standard deviations (`sd()`) from the mean. Each has trade-offs, but we won't
focus on those in this class._

**YOUR ANSWER GOES HERE:**

```{r}
ggplot(vehicles, aes(x = odometer, color = condition)) + geom_boxplot(coef = 1) + coord_cartesian(xlim = c(0, 250000)) # rescale the x-axis to compare different groups more easily

# fair and salvage cars has a higher overall odometer in terms of median, 
# max and span, while good, like new and excellent cars has lower overall odometer. 
# New cars, not surprisingly, has minimal overall odometer (close to zero).
```


Exercise 4
==========

Answer each question about advertisements for vehicles **in Berkeley**.

_Hint: You might want to get started by taking a subset. Watch out for missing
values._

1. How many advertisements are for vehicles in Berkeley?

2. How many of each `type` of car are there? Which type is the most common?

3. What's the median price (ignoring missing values) of each `type` of car?
   Which type has the highest median, and which has the lowest?

**YOUR ANSWER GOES HERE:**

```{r}
#number of advertisements for vehicles in Berkeley is 73
nrow(subset(vehicles, city == "Berkeley"))

#the number of cars of each type
summary(subset(vehicles, city == "Berkeley")['type'])
#we can see that "sedan" is the most common

berkeley = subset(vehicles, city == "Berkeley")
tapply(berkeley$price, berkeley$type, median, na.rm = TRUE)
#we can see that pickup has the highest median, and bus has the lowest median
```


Exercise 5
==========

1. Make a density plot of price. Use three separate lines for ads in San
   Francisco, San Jose, and Oakland (omit the other cities).

   _Hint: You can use the `droplevels()` function to drop factor levels that
   aren't present._

2. How do price distributions of the three cities compare?

3. Based on the plot, which of these cities have ads with extreme/anomalous
   prices? Isolate one of these ads. Does the extreme price seem accurate, or
   is it a mistake? Use the original title and text of the ad as evidence.

   _Hint 1: You can print the text of an ad in human-readable form with the
   `message()` function._

   _Hint 2: You can use the `stringr` package's `str_wrap()` function to wrap
   long strings (e.g., the ad text) for printing in the notebook._

   _Hint 3: The PDFLaTeX program that RMarkdown uses to knit PDFs only supports
   ASCII characters. Many of the advertisments contain non-ASCII characters. If
   you get a knit error like `! Package inputenc Error: Unicode character`, you
   probably printed an ad with non-ASCII characters._

   _To fix it, you can either comment out the line that prints the ad, or
   switch from PDFLaTeX to XeLaTeX or LuaLaTeX. See
   <https://bookdown.org/yihui/rmarkdown-cookbook/latex-unicode.html> for
   details about how to switch._


**YOUR ANSWER GOES HERE:**


```{r}
three_city = subset(vehicles, city == "Oakland"| city == "San Jose"| city == "San Francisco")
ggplot(three_city, aes(x = price, color = city)) + geom_density()

#the overall price of San Francisco and Oakland are lower 
# (as density for smaller prices are higher), 
# and the price for San Jose are higher (shown by the small climax around 40000)
# As the graph shows, San Francisco has some extreme prices 
# (demonstrated by small bulges for extreme high prices)

high_price = subset(three_city, price > 1e5)
high_price['title']
high_price['text']
# the extreme high prices are reasonable as the cars are luxury cars 
# (such as Ferrari, Rolls Royce, Aston Martin etc). 
# Moreover, the cars are all in good conditions, which makes it reasonable for high prices.
```







