---
title: "STAT 33B Workbook 12"
date: "Nov 19, 2020"
author: "Yuanrui Zhu (3034615728)"
output: pdf_document
---

This workbook is due __Nov 19, 2020__ by 11:59pm PT.

The workbook is organized into sections that correspond to the lecture videos
for the week. Watch a video, then do the corresponding exercises _before_
moving on to the next video.

Workbooks are graded for completeness, so as long as you make a clear effort to
solve each problem, you'll get full credit. That said, make sure you understand
the concepts here, because they're likely to reappear in homeworks, quizzes,
and later lectures.

As you work, write your answers in this notebook. Answer questions with
complete sentences, and put code in code chunks. You can make as many new code
chunks as you like.

In the notebook, you can run the line of code where the cursor is by pressing
`Ctrl` + `Enter` on Windows or `Cmd` + `Enter` on Mac OS X. You can run an
entire code chunk by clicking on the green arrow in the upper right corner of
the code chunk. 

Please do not delete the exercises already in this notebook, because it may
interfere with our grading tools.

You need to submit your work in two places:

* Submit this Rmd file with your edits on bCourses.
* Knit and submit the generated PDF file on Gradescope.

If you have any last-minute trouble knitting, **DON'T PANIC**. Submit your Rmd
file on time and follow up in office hours or on Piazza to sort out the PDF.


Tidy Data
=========

Watch the "Tidy Data" lecture video.

No exercises for this section.



Columns into Rows
=================

Watch the "Columns into Rows" lecture video.

No exercises for this section.



Rows into Columns
=================

Watch the "Rows into Columns" lecture video.



String Processing
=================

Watch the "String Processing" lecture video.


```{r, eval = FALSE}
#install.packages("tidyr")
```


## Exercise 1

Visit the [stringr documentation](https://stringr.tidyverse.org/).

How does the `str_sub` function work? Give 3 examples, including 1 that shows
how to use `str_sub` to reassign part of a string.

**YOUR ANSWER GOES HERE:**

"str_sub" gives the substring of the given string (vector of string), starting at the position of the second argument passed in and ending at the position of the third argument passed in. 

```{r}
library(tidyr)
library(stringr)
x = c("hello", "hi", "goodbye", "bye")
str_sub(x, 1, 2)
str_sub(x, -2, -1)
str_sub(x, 1, 1) = "xx" # reassign the first character to "x"
x
```


## Exercise 2

Complete the `table3` example from the lecture by showing the entire process
for converting `table3` into a tidy data frame.

_Hint: All of the functions needed to do this were mentioned in the lecture or
in other recent lectures._



```{r}
library(tidyr)
library(stringr)
#spliting the rate column into two seperate ones
splited = str_split_fixed(table3$rate, "/", 2)

#take the first two columns of the original table
truncated = table3[-3]

#combine the table3 with the seperate columns
combined = cbind(truncated, splited)

#name the third and fourth columns of the table
names(combined)[3] = "cases"
names(combined)[4] = "population"
combined
```



Regular Expressions
===================

Watch the "Regular Expressions" lecture video.

If you use RStudio, the RegExplain RStudio addin makes it easier to learn how
to use regular expressions. You can find information about how to install
RegExplain on the documentation page for stringr.

If you decide not to install RegExplain, there are many online regular
expression testers that can be helpful when learning. For example, I like
<https://regex101.com>.


## Exercise 3

The lecture video "Printing Output" described how R interprets backslashes in
strings as escape sequences. For instance, the string `"\t"` is a tab
character.

Because backslashes have a special meaning, to put a literal backslash in a
string, you have to write the backslash twice: `"\\"`.

Regular expressions also use backslash as a special character. In a regular
expression, putting a backslash in front of a metacharacter causes it to be
interpreted literally. For instance, the pattern `"\."` matches a single,
literal dot (rather than being a wildcard).

R's rule for backslashes interacts with regex's rule for backslashes in an
unfortunate way. Regex patterns in R are just strings, and R interprets `"\."`
(or backslash followed by any other character) as an escape sequence. Since we
need a literal backslash, we have to write `"\\."` in R. Then the regular
expression system sees this as `"\."`, and searches for a literal `"."`.

This interaction is especially bad if you want to search for a literal
backslash with a regular expression. You'd need to write `"\\\\"`!

As a remedy, R version 4.0 introduced _raw strings_. In a raw string, R always
interprets backslashes literally (rather than as escape sequences).

1. Raw strings are documented in `?Quotes`. Find the section in that file and
   read it. 

2. Give an example of creating a raw string.

3. Write a vectorized function `has_backslash` with parameter `x` that returns
   `TRUE` if `x` contains a backslash and `FALSE` otherwise. In your function,
   use `str_detect` with a raw string for the pattern.

**YOUR ANSWER GOES HERE:**

```{r}
# example of creating a raw string
r"{(\1\2)}"

# creating has_backslash function
has_backslash = function(x) {
  str_detect(x, r"(\\)")
}
x = "\b\\c"
has_backslash(x)
y = "qdfoqmef"
has_backslash(y)
```


## Exercise 4

Write a function `extract_phone` that extracts a phone number from a string.
Your function should return the phone number as a string in the format
`NNN-NNNN` without any other characters.

Test your function on the following strings:

```{r}
ex1 = "Phone: 555-2920"
ex2 = "Hi! The number you've called is 555-3131!"
ex3 = "The phone for unit 4342 is 555-9753."
```

_Hint 1: Use `str_match` to extract the number._

_Hint 2: Take advantage of non-numeric characters that mark the boundaries of a
phone number._

**YOUR ANSWER GOES HERE:**

```{r}
extract_phone = function(x) {
  str_match(x, "[0-9]{3}-[0-9]{4}")
}
example = c(ex1, ex2, ex3)
extract_phone(example)
```

