---
title: "STAT 33B Workbook 4"
date: "Sep 24, 2020"
author: "Yuanrui Zhu (3034615728)"
output: pdf_document
---

This workbook is due __Sep 24, 2020__ by 11:59pm PT.

The workbook is organized into sections that correspond to the lecture videos
for the week. Watch a video, then do the corresponding exercises _before_
moving on to the next video.

Workbooks are graded for completeness, so as long as you make a clear effort to
solve each problem, you'll get full credit. That said, make sure you understand
the concepts here, because they're likely to reappear in homeworks, quizzes,
and later lectures.

As you work, write your answers in this notebook. Answer questions with
complete sentences, and put code in code chunks. You can make as many new code
chunks as you like.

In the notebook, you can run the line of code where the cursor is by pressing
`Ctrl` + `Enter` on Windows or `Cmd` + `Enter` on Mac OS X. You can run an
entire code chunk by clicking on the green arrow in the upper right corner of
the code chunk. 

Please do not delete the exercises already in this notebook, because it may
interfere with our grading tools.

You need to submit your work in two places:

* Submit this Rmd file with your edits on bCourses.
* Knit and submit the generated PDF file on Gradescope.


R Graphics Overview
===================

Watch the "R Graphics Overview" lecture video.

No exercises for this section. Keep at it!


The Tidyverse
=============

Watch the "The Tidyverse" lecture video.


## Exercise 1

How many packages are in the Tidyverse? Explore the website to find out. You
can count the tidymodels packages as a single package.

YOUR ANSWER GOES HERE:

There are about 7 packages in the Tidyverse, they are:
-readr
-tibble
-purrr
-forcats
-ggplot2
-dplyr
-stringr


Tibbles
=======

Watch the "Tibbles" lecture video.

## Exercise 2

Read the documentation for the tibble package on the website.

1. Create a tibble with 4 rows and 3 columns from vectors. You can make up the
   data in the vectors. Use a different data type for each column.

2. Show how to convert the tibble to an ordinary data frame.

YOUR ANSWER GOES HERE:

```{r}
#install.packages("tidyr")
library(tibble)
column1 = c(1, 2, 3, 4)
column2 = c("a", "b", "c", "d")
column3 = c(TRUE, FALSE, TRUE, FALSE)
t = tibble(column1, column2, column3)
class(as.data.frame(t))
```



The Grammar of Graphics
=======================

Watch the "The Grammar of Graphics" lecture video.


## Exercise 3

Use ggplot2 and the dogs data to make a scatterplot that shows the relationship
between height and weights. In 2-3 sentences, discuss any patterns you see in
the plot.

YOUR ANSWER GOES HERE:

```{r}
dogs = readRDS("dogs.rds")
library(ggplot2)
ggplot(dogs, aes(x = height, y = weight)) + geom_point()
```

I discover that there is a strong positive correlation between a dog's height and its weight. That is, the taller the dog, the heavier it becomes.


## Exercise 4

Use ggplot2 and the dogs data to make a histogram of longevity. How long do
most dogs typically live? How spread out is the distribution of lifespans?

YOUR ANSWER GOES HERE:

```{r}
ggplot(dogs, aes(x = longevity)) + geom_histogram()
```

From the histogram, we can see most dogs lives between 10-12,5 years old. The spread is quite large, from less than 3 to approximately 20. The distribution is roughly normal, with two pinnacles around 8 and 12.5.


Saving Plots
============

Watch the "Saving Plots" lecture video.

No exercises for this section. Almost done!


Customizing Plots
=================

Watch the "Customizing Plots" lecture video.

## Exercise 5

Revisit your scatterplot from Exercise 3. Make the size of each point
correspond to the size of the dog. Make the color of each point correspond to
how good the dog is with kids. Add an appropriate title and labels.

_Hint: A "low" score for kids means the dog is bad with kids._

YOUR ANSWER GOES HERE:

```{r}
ggplot(dogs, aes(x = height, y = weight)) + geom_point(aes(color = kids, size = weight)) +
  labs(title = "Dog's size relative to dogs' weight")

```



## Exercise 6

Use ggplot2 and the dogs data to answer each of the following questions.

1. Is there a relationship between how long dogs live and how big (in any
   sense) they are?

2. Do small dogs tend to be good with kids? If not, does size seem to be
   related to how good dogs are with kids at all?

3. Is there a relationship between size and grooming needs?

_Hint: The table from the notes for the next lecture video might help you
decide which plots to use for these questions._

YOUR ANSWER GOES HERE:


```{r}
ggplot(dogs, aes(x = longevity, y = weight)) + geom_point()
ggplot(dogs, aes(x = weight, y = kids)) + geom_point()
ggplot(dogs, aes(x = weight, y = grooming)) + geom_point()
```
There is a strong negative relationship between the dog size and its longevity. Small dogs don't tend to be good with kids (it seems kids and weight do not correlate to each other very much). There is barely no relationship between size and grooming needs.


Exploratory Data Analysis
=========================

This lecture video is **OPTIONAL**. You can skip it if you like.

The "Exploratory Data Analysis" video discusses how to choose an appropriate
plot for a given set of columns.

No exercises for this section.
