---
title: "STAT 33B Workbook 7"
date: "Oct 15, 2020"
author: "Yuanrui Zhu (3034615728)"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

This workbook is due __Oct 15, 2020__ by 11:59pm PT.

The workbook is organized into sections that correspond to the lecture videos
for the week. Watch a video, then do the corresponding exercises _before_
moving on to the next video.

Workbooks are graded for completeness, so as long as you make a clear effort to
solve each problem, you'll get full credit. That said, make sure you understand
the concepts here, because they're likely to reappear in homeworks, quizzes,
and later lectures.

As you work, write your answers in this notebook. Answer questions with
complete sentences, and put code in code chunks. You can make as many new code
chunks as you like.

In the notebook, you can run the line of code where the cursor is by pressing
`Ctrl` + `Enter` on Windows or `Cmd` + `Enter` on Mac OS X. You can run an
entire code chunk by clicking on the green arrow in the upper right corner of
the code chunk. 

Please do not delete the exercises already in this notebook, because it may
interfere with our grading tools.

You need to submit your work in two places:

* Submit this Rmd file with your edits on bCourses.
* Knit and submit the generated PDF file on Gradescope.

If you have any last-minute trouble knitting, **DON'T PANIC**. Submit your Rmd
file on time and follow up in office hours or on Piazza to sort out the PDF.


For-loops
=========

Watch the "For-loops" lecture video.

No exercises for this section.



Loop Indices
============

Watch the "Loop Indices" lecture video.

No exercises for this section.



While-loops
===========

Watch the "While-loops" lecture video.

No exercises for this section.



Preallocation
=============

Watch the "Preallocation" lecture video.

## Exercise 1

Use the microbenchmark package to benchmark the "BAD" and "GOOD" example from
the lecture video.

Benchmark with three different values of `n` (testing both the "BAD" and "GOOD"
example for each value). About how much faster is the "GOOD" example?

**YOUR ANSWER GOES HERE:**

```{r}
#install.packages("microbenchmark")
library(microbenchmark)

bad = function(n) {
   x = c()
   for (i in 1:n) {
      x = c(x, i * 2)
   }
   x
}

good = function(n) {
   x = numeric(n)
   for (i in seq_len(n)) {
      x[i] = i * 2
   }
}

#check with 1e1 iterations
microbenchmark(bad(1e1), times = 100L)
microbenchmark(good(1e1), times = 100L)

#check with 1e2 iterations
microbenchmark(bad(1e2), times = 1000L)
microbenchmark(good(1e2), times = 1000L)

#check with 1e3 iterations
microbenchmark(bad(1e3), times = 1000L)
microbenchmark(good(1e3), times = 1000L)

#From the test we can see that the good example is about 
#10-100 times faster than the bad example

```


Loops Example
=============

Watch the "Loops Example" lecture video.

## Exercise 2

Write a function that returns the first `n + 1` positions of a 3-dimensional
discrete random walk. Return the `x`, `y`, and `z` coordinates in a data frame
with columns `x`, `y`, and `z`. Your function should have a parameter `n` that
controls the number of steps.

_Hint: For efficiency, use vectors for `x`, `y`, and `z`. Wait to combine them
into a data frame until the very last line of your function._

**YOUR ANSWER GOES HERE:**

```{r}
ThreeDimRandomWalk = function(n) {
   xyz = sample(c(0, 1, 2), n+1, replace = TRUE)  
   move = sample(c(-1, 1), n+1, replace = TRUE)
   x <- numeric(n+1)
   y <- numeric(n+1)
   z <- numeric(n+1)
   for (i in seq_len(n+1)) {
      if (xyz[i] == 0) { # x
         x[i + 1] = x[i] + move[i]
         y[i + 1] = y[i]
         z[i + 1] = z[i]
      } else if (xyz[i] == 1) { # y
         x[i + 1] = x[i]
         y[i + 1] = y[i] + move[i]
         z[i + 1] = z[i]
      } else {
         x[i + 1] = x[i]
         y[i + 1] = y[i]
         z[i + 1] = z[i] + move[i]
      }
   }
   result <- data.frame("x" = x, "y" = y, "z" = z)
   result
}
ThreeDimRandomWalk(10)

```


Recursion
=========

Watch the "Recursion" lecture video.


## Exercise 3

1. Use the microbenchmark package to benchmark `find_fib()` and `find_fib2()`
   for `n` equal to 1 through 30.

2. Collect the median timings for each into a data frame with a columns `time`,
   `n`, and `function`. The data frame should have 60 rows (30 for each
   function).

3. Use ggplot2 to make a line plot of `n` versus `time`, with a separate line
   for each `function`.

4. Comment on the the shapes of the lines. Does the computation time grow at
   the same rate (as `n` increases) for both functions?

**YOUR ANSWER GOES HERE:**

```{r}
find_fib = function(n) {
  if (n == 1 | n == 2)
    return (1)
  
  find_fib(n - 2) + find_fib(n - 1)
}

find_fib2 = function(n, fib = c(1, 1)) {
  len = length(fib)
  if (n <= len)
    return (fib[n])
  
  fib = c(fib, fib[len - 1] + fib[len])
  find_fib2(n, fib)
}
#since 30 is too large for my computer (it crashes when I tried to run with 30 iterations),
#I choose to run with 20 iterations for each functions
second = numeric(40)
name = character(40)
n = numeric(40)
for (i in 1:20) {
   second[i] = summary(microbenchmark(find_fib(i), times = 1000L, unit = 'ms'))[1, "median"]
   name[i] = 'find_fib()'
   n[i] = i
}
for (i in 1:20) {
   second[i+20] = summary(microbenchmark(find_fib2(i), times = 1000L, unit = 'ms'))[1, "median"]
   name[i+20] = 'find_fib2()'
   n[i+20] = i
}
data_fib <- data.frame("name" = name, "n" = n, "time" = second)
data_fib
#install.packages("ggplot2")
library(ggplot2)
ggplot(data_fib, aes(x = n, y = time, color = name)) + geom_line()

#from the plot we an see that the function does not grow in the same rate. 
# find_fib() grows exponentially large as n gets large, where find_fib2() 
#takes about constant time

```


Developing Iterative Code
=========================

Watch the "Developing Iterative Code" lecture video.

No exercises for this section. All done!
