---
title: "STAT 33B Workbook 8"
date: "Oct 22, 2020"
author: "Yuanrui Zhu (3034615728)"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

This workbook is due __Oct 22, 2020__ by 11:59pm PT.

The workbook is organized into sections that correspond to the lecture videos
for the week. Watch a video, then do the corresponding exercises _before_
moving on to the next video.

Workbooks are graded for completeness, so as long as you make a clear effort to
solve each problem, you'll get full credit. That said, make sure you understand
the concepts here, because they're likely to reappear in homeworks, quizzes,
and later lectures.

As you work, write your answers in this notebook. Answer questions with
complete sentences, and put code in code chunks. You can make as many new code
chunks as you like.

In the notebook, you can run the line of code where the cursor is by pressing
`Ctrl` + `Enter` on Windows or `Cmd` + `Enter` on Mac OS X. You can run an
entire code chunk by clicking on the green arrow in the upper right corner of
the code chunk. 

Please do not delete the exercises already in this notebook, because it may
interfere with our grading tools.

You need to submit your work in two places:

* Submit this Rmd file with your edits on bCourses.
* Knit and submit the generated PDF file on Gradescope.

If you have any last-minute trouble knitting, **DON'T PANIC**. Submit your Rmd
file on time and follow up in office hours or on Piazza to sort out the PDF.


Printing Output
===============

Watch the "Printing Output" lecture video.

## Exercise 1

The `scan` function provides a way to collect _input_ from the user.

Write a program that loops endlessly and:

1. Asks the user to input their name.
2. Uses `scan` to collect their input.
3. Prints `"Hello, NAME!"` where `NAME` is replaced by the collected name.

The program should exit the loop (and quit) if the user enters the name `quit`.

**YOUR ANSWER GOES HERE:**

```{r, eval = FALSE}  
# Method 1
repeat {
  if (!name == 'quit')
  cat("Hello", scan(file = "", what = "character", n = 1))
}
```


```{r, eval = FALSE}
# Method 2
repeat {
  name = readline(prompt = "Please enter your name: ")
  if (name == 'quit') break 
  print(paste('Hello,',name,'!'))
}
```


Messages, Warnings, and Errors
==============================

Watch the "Messages, Warnings, and Errors" lecture video.

## Exercise 2

A vectorized implementation of the `to_kelvin` function from Workbook 6 is:
```{r, eval = FALSE}
to_kelvin = function(temperature, unit) {
  unit = match.arg(unit, c("celsius", "fahrenheit"), several.ok = TRUE)

  # First convert Fahrenheit to Celsius.
  is_f = unit == "fahrenheit"
  temperature[is_f] = (temperature[is_f] - 32) * 5 / 9

  temperature + 273.15
}
```

Write a modified version of `to_kelvin` that checks for potential problems. In
particular, your version should check the assumptions that:

* `temperature` is numeric.
* `temperature` and `unit` are the same length, or `unit` has length 1.

Your version should raise an error (with a descriptive message) if either of
these assumptions don't hold.

Test your function to show that it checks for potential problems. You can use
`error = TRUE` on an RMarkdown code chunk to allow errors when knitting.

**YOUR ANSWER GOES HERE:**

```{r, eval = FALSE}
to_kelvin = function(temperature, unit) {
  unit = match.arg(unit, c("celsius", "fahrenheit"), several.ok = TRUE)
  
  if (!is.numeric(temperature)) {
    stop("Temperature is not numeric")
  }
  
  if (!length(temperature) == length(unit)) {
    stop("Temperature and Unit are not in the same length")
  }
  
  # First convert Fahrenheit to Celsius.
  is_f = unit == "fahrenheit"
  temperature[is_f] = (temperature[is_f] - 32) * 5 / 9

  temperature + 273.15
}
```


Handling Errors
===============

Watch the "Handling Errors" lecture video.

No exercises for this section.


Global Options
==============

Watch the "Global Options" lecture video.

## Exercise 3

Skim `?options` and `?Startup`.

Create or edit your `.Rprofile` file to set an option (or several options).

Check that your option is actually set when you restart R (you can call
`options` without any arguments to see your current options).

In your answer here, describe which option you set and include the code you
added to `.Rprofile`.

**YOUR ANSWER GOES HERE:**

```{r, eval = FALSE}
# Put your new .Rprofile code here.
file.edit(file.path("~", ".Rprofile")) # edit .Rprofile in HOME
options(papersize="a4")
options(editor="notepad")
options(pager="internal")
```



Preventing Bugs
===============

Watch the "Preventing Bugs" lecture video.

No exercises for this section.


The R Debugger
==============

Watch the "The R Debugger" lecture video.

No exercises for this section.



Other Debugging Functions
=========================

Watch the "Other Debugging Functions" lecture video.

No exercises for this section. You're done!
